### 2017-08-30 status.tex
tweaked a section header

\subsection{Problems and limitations}
The big problem with this model, which we identified after we got feedback on the first draft, is that the block size process model does not take into account that excess transactions that arrive during one block spill over into the next block. So all observed block sizes will be lower than the block size limit for that particular block. For example is every block has a 1 MB block size limit, we would never observe a block with more than 1 MB of transactions, even when the limit is routinely being reach. What $d_k$ represents is not the total amount of transaction data that was {\it submitted} to the block chain after block $k-1$ arrived but before block $k$, instead it represents the total amount of transaction data {\it accepted} by the block chain in block $k$.

>>>>

\subsection{Problems and solutions}
The big problem with this model, which we identified after we got feedback on the first draft, is that the block size process model does not take into account that excess transactions that arrive during one block spill over into the next block. So all observed block sizes will be lower than the block size limit for that particular block. For example is every block has a 1 MB block size limit, we would never observe a block with more than 1 MB of transactions, even when the limit is routinely being reach. What $d_k$ represents is not the total amount of transaction data that was {\it submitted} to the block chain after block $k-1$ arrived but before block $k$, instead it represents the total amount of transaction data {\it accepted} by the block chain in block $k$.
